---
title: "Report"
author: ""
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
  rm(list = ls())
  graphics.off()
  library(tibble)
  library(ggplot2)
  setwd(getwd())
```

```{r, include=FALSE}
  source("variables.R",local = knitr::knit_global())
```

This report represents a statistical analysis of the main thermodynamic variables. The figures below show the time evolution of Volume, temperature, pressure and density followed by the linear regression (red line).

## Parameters

```{r, echo=FALSE}
  cat(paste("Host:",var_host))
  cat(paste("Date:",var_date))
  cat(paste("Ensemble:",ensemble))
  cat(paste("Timestep:",timestep,"ps"))
  cat(paste("Number of atoms:",natoms))
```

## Volume

```{r, echo=FALSE}
  df2 %>% ggplot(aes(x=TIME,y=VOLUME))+
  geom_line(color="black")+
  geom_smooth(method = "lm",color="red")+
  theme_bw()+theme(panel.grid = element_blank())+
  labs(x="Time (ps)",y=expression(paste("Volume ",(ring(A)^3))))
```

Here is the statistical values of the volume of the unit cell.

```{r fit_volume, echo=FALSE}
  summary(df2$VOLUME)
```

## Temperature

```{r, echo=FALSE}
  df2 %>% ggplot(aes(x=TIME,y=TEMPERATURE))+
  geom_line(color="black")+
  geom_smooth(method = "lm",color="red")+
  theme_bw()+theme(panel.grid = element_blank())+
  labs(x="Time (ps)",y=expression(paste("Temperature (K)")))
```

Here is the statistical values of the temperature.

```{r FIT_TEMPERATURE, echo=FALSE}
  summary(df2$TEMPERATURE)
```

## Pressure

```{r, echo=FALSE}
  df2 %>% ggplot(aes(x=TIME,y=PRESSURE))+
  geom_line(color="black")+
  geom_smooth(method = "lm",color="red")+
  theme_bw()+theme(panel.grid = element_blank())+
  labs(x="Time (ps)",y=expression(paste("Pressure (atm)")))
```

Here is the statistical values of the pressure.

```{r fit_pressure, echo=FALSE}
  summary(df2$PRESSURE)
```

## Energy

```{r, echo=FALSE}
  df2 %>% ggplot(aes(x=TIME,y=ENERGY))+
  geom_line(color="black")+
  geom_smooth(method = "lm",color="red")+
  theme_bw()+theme(panel.grid = element_blank())+
  labs(x="Time (ps)",y=expression(paste("Energy (kcal/mol)")))
```

Here is the statistical values of the energy.

```{r FIT_ENERGY, echo=FALSE}
  summary(df2$ENERGY)
```
