---
title: "Report"
author: ""
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
  rm(list = ls())
  graphics.off()
  library(tidyverse)
  setwd(getwd())
```

```{r, include=FALSE}
  source("import_and_clean_data.R",local = knitr::knit_global())
  source("model.R",local = knitr::knit_global())
```

This report represents a statistical analysis of the main thermodynamic variables. The figures below show the time evolution of volume, temperature, pressure and energy, followed by a smooth fitting function (red line).

## Parameters

```{r, echo=FALSE}
  cat("Ensemble:",head$ensemble[1],head$ensemble[2])
  cat("System:",system$X4,"atoms")
  if (head$ensemble[1]=="npt") {
    cat("pressure:",head$pressure[1],"atm")
  } 
  if (head$ensemble[1]=="npt"| head$ensemble[1]=="nvt") {
    cat("temperature:",head$temperature[1],"K")
  }
  cat("timestep:",head$timestep[1],"ps")
  cat("time-scale:",head$timestep[1]*head$nstep[1],"ps")
```

# Here is the summary of some thermodynamic variables.

```{r, statistics, echo=FALSE}
  print(data_mean)
```

## volume

```{r volume, echo=FALSE}
  thermo %>%
  filter(data=='volume') %>%
    ggplot(aes(x=time,y=value))+
    geom_line(color="black")+
    geom_smooth(color="red",se=T)+
    labs(x="time (ps)",y=expression(paste("volume ",(ring(A)^3))))
```

## temperature

```{r temperature, echo=FALSE}
  thermo %>%
  filter(data=='temperature') %>%
    ggplot(aes(x=time,y=value))+
    geom_line(color="black")+
    geom_smooth(color="red",se=T)+
    labs(x="time (ps)",y=expression(paste("temperature (K)")))
```

## pressure

```{r pressure, echo=FALSE}
  thermo %>%
  filter(data=='pressure') %>%
    ggplot(aes(x=time,y=value))+
    geom_line(color="black")+
    geom_smooth(color="red",se=T)+
    labs(x="time (ps)",y=expression(paste("pressure", (atm))))
```

## energy

```{r energy, echo=FALSE}
  thermo %>%
  filter(data=='energy') %>%
  ggplot(aes(x=time,y=value))+
  geom_line(color="black")+
  geom_smooth(color="red",se=T)+
  labs(x="time (ps)",y=expression(paste("energy", (kcal/mol))))
```

## density

```{r density, echo=FALSE}
  thermo %>%
  filter(data=='density') %>%
  ggplot(aes(x=time,y=value))+
  geom_line(color="black")+
  geom_smooth(color="red",se=T)+
  labs(x="time (ps)",y=expression(paste("density", (g/cm^3))))
```

## Maximum force

```{r force, echo=FALSE}
  value_max %>%
  ggplot(aes(x=time,y=fmax))+
  geom_line(color="black")+
  geom_smooth(color="red",se=T)+
  labs(x="time (ps)",y=expression(paste("F_max", (kcal/mol.A))))
```

# Gaussiana distribution of the thermodynamic values.

```{r, echo=FALSE}
  ggplot()+
    geom_histogram(data=filter(thermo,data=='volume'),mapping=aes(value),
                   binwidth = as.integer((data_mean[5,5]-data_mean[5,4])/30))+
    geom_histogram(data=filter(thermo,data=='temperature'),mapping=aes(value),
                   binwidth = as.integer((data_mean[4,5]-data_mean[4,4])/30))+
    geom_histogram(data=filter(thermo,data=='pressure'),mapping=aes(value),
                   binwidth = as.integer((data_mean[3,5]-data_mean[3,4])/30))+
    geom_histogram(data=filter(thermo,data=='energy'),mapping=aes(value),
                   binwidth = as.integer((data_mean[2,5]-data_mean[2,4])/30))+
    geom_histogram(data=filter(thermo,data=='density'),mapping=aes(value),
                   binwidth = 0.005)+
    facet_wrap(~data,nrow=3,scales = "free")
```